Notes on Validated Model Counting

### 2021-04-15 doc/mc-notes.tex
New notation
Added

\newcommand{\one}{\mbox{\bf 1}}
\newcommand{\zero}{\mbox{\bf 0}}
\newcommand{\leafone}{L_1}
\newcommand{\leafzero}{L_0}
\newcommand{\booland}{\land}
\newcommand{\boolor}{\lor}
\newcommand{\boolxor}{\oplus}
\newcommand{\boolnot}{\neg}
\newcommand{\tautology}{\top}
\newcommand{\nil}{\bot}
\newcommand{\obar}[1]{\overline{#1}}
\newcommand{\ite}{\mbox{\it ITE}}

@@

\newcommand{\subs}[2]{[#1/#2]}
\newcommand{\substrue}[1]{\subs{#1}{\tautology}}
\newcommand{\subsfalse}[1]{\subs{#1}{\false}}
\newcommand{\subsflip}[1]{\subs{#1}{\obar{#1}}}

@@

A {\em proper} ITE graph is one for which the incoming \ifarg{} arc for every operator node is
from an input node.  That is, the result of one $\ite$ operation can
serve as the ``then'' or ``else'' argument to another $\ite$
operation, but not for the ``if'' argument.

When describing proper ITE graphs, we refer to constant and input
nodes by their associated value or variable.  An operator node is described by an expression of the form
$\ite(x, v_t, v_e)$, where $v_t$ and $v_e$ are the
nodes corresponding to the \thenarg{} and \elsearg{} inputs, respectively.

We can define the function $\depend$ mapping each node
$v$ in a proper ITE graph to the set of variables on which it logically depends.  This can be expressed recursively as
\begin{eqnarray}
\depend(\tautology) & = & \emptyset \label{eqn:depend:true}\\
\depend(\nil) & = & \emptyset \label{eqn:depend:false}\\
\depend(x) & = & \{x \} \label{eqn:depend:variable}\\
\depend(\ite(x, v_t, v_e)) & = & \{ x \} \cup \depend(v_t) \cup \depend(v_e) \label{eqn:depend:ite}
\end{eqnarray}

@@

A {\em free} ITE graph is a proper ITE graph satisfying the added
property that for every operator node $v = \ite(x, v_t, v_e)$, its
incoming \thenarg{} and \elsearg{} arcs must be from nodes such that
$x \not \in \depend(v_t)$ and $x \not \in \depend(v_e)$.

>>>>

\newcommand{\one}{\mbox{\bf 1}}
\newcommand{\zero}{\mbox{\bf 0}}
\newcommand{\leafone}{L_1}
\newcommand{\leafzero}{L_0}
\newcommand{\booland}{\land}
\newcommand{\boolor}{\lor}
\newcommand{\boolxor}{\oplus}
\newcommand{\boolnot}{\neg}
%\newcommand{\tautology}{\top}
%\newcommand{\nil}{\bot}
\newcommand{\tautology}{1}
\newcommand{\nil}{0}
\newcommand{\obar}[1]{\overline{#1}}
\newcommand{\ite}{\mbox{\it ITE}}

@@

\newcommand{\subs}[2]{[#2/#1]}
\newcommand{\substrue}[1]{\subs{#1}{\tautology}}
\newcommand{\subsfalse}[1]{\subs{#1}{\false}}
\newcommand{\subsflip}[1]{\subs{#1}{\obar{#1}}}

@@

An {\em input-controlled} ITE graph is one for which the incoming \ifarg{} arc for every operator node is
from an input node.  That is, the result of one $\ite$ operation can
serve as the ``then'' or ``else'' argument to another $\ite$
operation, but not for the ``if'' argument.

When describing input-controlled ITE graphs, we refer to constant and input
nodes by their associated value or variable.  An operator node is described by an expression of the form
$\ite(x, v_t, v_e)$, where $v_t$ and $v_e$ are the
nodes corresponding to the \thenarg{} and \elsearg{} inputs, respectively.

We can define the function $\depend$ mapping each node
$v$ in an input-controlled ITE graph to the set of variables on which it logically depends.  This can be expressed recursively as
\begin{eqnarray}
\depend(\tautology) & = & \emptyset \label{eqn:depend:true}\\
\depend(\nil) & = & \emptyset \label{eqn:depend:false}\\
\depend(x) & = & \{x \} \label{eqn:depend:variable}\\
\depend(\ite(x, v_t, v_e)) & = & \{ x \} \cup \depend(v_t) \cup \depend(v_e) \label{eqn:depend:ite}
\end{eqnarray}

@@

A {\em free} ITE graph is an input-controlled ITE graph satisfying the added
property that for every operator node $v = \ite(x, v_t, v_e)$, its
incoming \thenarg{} and \elsearg{} arcs must be from nodes such that
$x \not \in \depend(v_t)$ and $x \not \in \depend(v_e)$.
